Runaway and Hypervelocity Stars from Compact Object Encounters in Globular Clusters

### 2024-02-14 src/tex/ms.tex
Updated Zenodo link, fixed figure caption.

\begin{figure*}
    \script{rgc-z.py}
    \begin{centering}
        \includegraphics[width=0.9\linewidth]{figures/rgc-z_S.pdf}
        \caption{
            Histograms (top) and velocity quantiles (bottom) for the synthetic stellar ejecta.
            The left (right) plots show the profile over radial distance from the galactic center $r_{\rm gc}$ (distance from the galactic plane $Z$).
            The quantiles in the lower plots are calculated from the present-day velocities of our population.
            The red dots show the $r_{\rm gc}$ ($Z$) positions of the MWGCs from our composite \citet{2018MNRAS.478.1520B}+\citet{2010arXiv1012.3224H} catalog, arbitrarily spread in the vertical dimension.
        }
        \label{fig:rgc-z}
    \end{centering}
\end{figure*}

>>>>

\begin{figure*}
    \script{rgc-z.py}
    \begin{centering}
        \includegraphics[width=0.9\linewidth]{figures/rgc-z_S.pdf}
        \caption{
            Histograms (top) and velocity quantiles (bottom) for the synthetic stellar ejecta.
            The left (right) plots show the profile over radial distance from the galactic center $r_{\rm gc}$ (distance from the galactic plane $Z$).
            The quantiles in the lower plots are calculated from the present-day velocities of our population.
            The red dots show the MWGCs from our composite \citet{2018MNRAS.478.1520B}+\citet{2010arXiv1012.3224H} catalog.
        }
        \label{fig:rgc-z}
    \end{centering}
\end{figure*}
